---
title: "Homework 6"
author: "Mari Sanders"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(purrr)
library(glmnet)
set.seed(10)
```

# Problem 1 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}

betas <- function(lm) {
    broom::tidy(lm) %>% 
    pull(estimate) %>% 
    prod %>% log()
}
r_squareds <- function(lm) {
  broom::glance(lm) %>% 
    pull(r.squared) 
}

boots <- 
  weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax~tmin, data = .)), 
    log_betas = map(models, betas), 
    r_squared = map(models, r_squareds)
  )

r_squared_betas <- 
  boots %>% 
  unnest(log_betas:r_squared) %>% 
  select(-strap)

r_squared_betas %>% pull(log_betas) %>% 
  quantile(probs = c(0.025, 0.975))

r_squared_betas %>% pull(r_squared) %>% 
  quantile(probs = c(0.025, 0.975))


ggplot(r_squared_betas, aes(x = log_betas)) + geom_density()

ggplot(r_squared_betas, aes(x = r_squared)) + geom_density()
```



# Problem 2 

Data Cleaning 

```{r}
homicide_df <- read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  filter(victim_race != "NA") %>% 
  janitor::clean_names() %>% 
  unite(city_state, c(city, state), sep = ", ") %>% 
  filter(city_state != "Dallas, TX", 
         city_state != "Phoenix, AZ", 
         city_state != "Kansas City, MO", 
         city_state != "Tulsa, AL",
         victim_race %in% c("White", "Black"),
         victim_age != "Unknown"
  ) %>%
  mutate(victim_age = as.numeric(victim_age), 
           resolved = as.numeric(disposition == "Closed by arrest"), 
        victim_race = fct_relevel(victim_race, "White")) %>% 
  select(city_state, resolved, victim_age, victim_race, victim_sex) 
```

Baltimore 

```{r}
logistic <- 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

broom::tidy(logistic, conf.int = TRUE) %>% 
  mutate(OR = exp(estimate), 
         conf_low = exp(conf.low), 
         conf_high = exp(conf.high)) %>% 
  select(term, log_OR = estimate, OR, conf_low, conf_high) %>% 
  filter(term == "victim_sexMale") %>% 
  knitr::kable(digits = 3)
```

In Baltimore, homicides of male victims were 0.426 times more likely to be unsolved compared to homicides of female victims after adjusting for all other variables. 

```{r}
city_results <- homicide_df %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(
    model = map(data, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = "binomial")),
    results = map(model, broom::tidy, conf.int = TRUE)) %>%
  unnest(results) %>%
  mutate(OR = exp(estimate), 
         conf_low = exp(conf.low), 
         conf_high = exp(conf.high)) %>% 
  select(city_state, term, OR, conf_low, conf_high) %>%
   filter(term == "victim_sexMale") 

city_results %>% knitr::kable(digits = 3)
```

```{r}
city_results %>% 
  ggplot(aes(x = fct_reorder(city_state, OR), y = OR)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  labs(
    title = "Solved homicides, Male vs. Female Victims",
    x = "City", 
    y = "Adjusted Odds Ratio"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

All of the cities, except for Tulsa, Atlanta, Richmond, Nashville, Fresno, Stockton, and Albuquerque have an adjusted odds ratio less than 1. This means that males in all cities except for these are more likely to have unsolved homicides than females. 

# Problem 3 

```{r}
birthweight <- read_csv("data/birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex), 
         frace = as.factor(frace), 
         mrace = as.factor(mrace), 
         malform = as.factor(malform))

birthweight %>% 
  is.na() %>% 
  summary()
```

There are no missing values in this dataset. 

```{r}
x <- birthweight %>% 
  select(-bwt) %>% data.matrix()
y <- birthweight %>% 
  select(bwt) %>% pull()
cv_model <- cv.glmnet(x,y, alpha = 1)
best_lambda <- cv_model$lambda.min
plot(cv_model)
```

```{r}
best_model <- glmnet(x, y, alpha = 1, lambda = best_lambda)
coef(best_model)
```

Used lasso to find the most important coefficients 

```{r}
birthweight_model_adjusted <- 
  lm(bwt~ babysex + bhead + blength + delwt  + fincome + frace + gaweeks + menarche + mheight + momage + mrace + parity + smoken + wtgain, data = birthweight)
summary(birthweight_model_adjusted)
```

```{r}
birthweight %>%
  add_predictions(birthweight_model_adjusted) %>%
  add_residuals(birthweight_model_adjusted) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() 
```

```{r}
main_effects <- 
  lm(bwt ~ blength + gaweeks, data = birthweight)

interactions <- 
  lm(bwt ~bhead + blength + babysex + bhead*blength*babysex, data = birthweight)
```

```{r}
cv_df <- 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble), 
    test = map(test, as_tibble)
  ) %>% 
  mutate(my_model = map(train, \(df) lm(bwt~ babysex + bhead + blength + delwt  + fincome + frace + gaweeks + menarche + mheight + momage + mrace + parity + smoken + wtgain, data = df)),
    main_effects = map(train, \(df) lm(bwt ~ blength, gaweeks, data = df)), 
         interactions = map(train, \(df) lm(bwt ~bhead + blength + babysex + bhead*blength*babysex, data = df))) %>% 
  mutate(
    rmse_mymodel = map2_dbl(my_model, test, \(mod, df) rmse(model = mod, data = df)), 
    rmse_maineffects = map2_dbl(main_effects, test, \(mod, df) rmse(model = mod, data = df)), 
    rmse_interactions = map2_dbl(interactions, test, \(mod, df) rmse(model = mod, data = df))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(everything(), 
               names_to = "model", 
               values_to = "rmse", 
               names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

